The Shape Matching Element Method for Meshless Animation of NURBs Models

### 2021-01-24 paper/sections/methods.tex
finished rough draft of the network flow stuff. its rough alright

From the set of blending weights we seek to construct a set of candidate deformation origins and then produce a set of deformation origins, $\XBs$, adhering to the outlined requirements. This set of candidate origins is identified by examining the unique combinations of weight assignments for the quadrature points. For each $\refX_j$, we form a set $\mathbf{c}\left(\refX_j\right)$ with $c_i\left(\refX_j\right)= 1-\delta_{\bld_i\left(\refX_j\right),0}$ where $\delta_{x,0}$ is the Kronecker delta. This produces a binary code for each quadrature point that identifies the parts to which this point has nonzero weights. We use each unique binary code as a deformation origin candidate.

@@

Consider a directed bipartite graph $G=(V = A \cup B,E)$ where each node in $A$ corresponds to a deformation origin candidate and each node in $B$ represents a part. $E$ is the set of edges connecting nodes in $A$ to $B$ where each origin has an edge to every part with which it attempts to associate. We augment $G$ to form $G'=(V' = A \cup B \cup \{s,t\}, E')$ where $V'$  is the new set of nodes now containing the source, $s$, and sink, $t$, nodes. $E'$ is the augmented set of nodes connecting $s$ to each candidate in $A$ and connecting each part in $B$ to the sink $t$. Each edge $(i,j) \in E'$ has an associated flow $f_{ij}$ and capacity constraint $u_{ij}$, and each edge in $E'$ also has a cost $c_{ij}$. The principal constraint for this network flow problem is the conservation constraint, meaning that the net flow for all nodes in $V$ is zero.

First, we constrain all flow values to be integral and place a capacity of $1$ on the edges from $B$ to $t$. This has the effect of enforcing that any part node in $B$ receives flow from a single edge, and as a consequence each part may only be associated with a single deformation origin.  With the specified network and constraints, we solve this problem with an integer constrained linear program. We choose $\XBs$ to be all nodes in $A$ that have an outgoing flow of at least $1$.

>>>>

From the set of blending weights we seek to construct a set of candidate deformation origins and then produce a set of deformation origins, $\XBs$, adhering to the outlined requirements. This set of candidate origins is identified by examining the unique combinations of weight assignments for the quadrature points. For each $\refX_j$, we form a set $\mathbf{b}\left(\refX_j\right)$ with $b_i\left(\refX_j\right)= 1-\delta_{\bld_i\left(\refX_j\right),0}$ where $\delta_{x,0}$ is the Kronecker delta. This produces a binary code for each quadrature point that identifies the parts to which this point has nonzero weights. We use each unique binary code as a deformation origin candidate.

@@

Consider a directed bipartite graph $G=(V = A \cup B,E)$ where each node in $A$ corresponds to a deformation origin candidate and each node in $B$ represents a part. $E$ is the set of edges connecting nodes in $A$ to $B$ where each origin has an edge to every part with which it attempts to associate. We augment $G$ to form $G'=(V' = A \cup B \cup \{s,t\}, E')$ where $V'$  is the new set of nodes now containing the source, $s$, and sink, $t$, nodes. $E'$ is the augmented set of nodes connecting $s$ to each candidate in $A$ and connecting each part in $B$ to the sink $t$. Each edge $(i,j) \in E'$ has an associated flow $f_{ij}$ and capacity constraint $u_{ij}$, and each edge in $E$ also has a cost $c_{ij}$. The principal constraint for this network flow problem is the conservation constraint, meaning that the net flow for all nodes in $V$ is zero.

Next, we constrain all flow values to be integral and place a capacity of $1$ on the edges from $B$ to $t$. This has the effect of enforcing that any part node in $B$ receives flow from a single edge, and as a consequence each part may only be associated with a single deformation origin. The last step is to specify the costs on the edges, $E$, between the origin candidates and the parts. Costs are assigned in such a way that for each unique binary code, $\mathbf{b}$, we sum the set of weights for each quadrature point associated with this code. Since for each non-zero $b_i$, we have an edge connecting the node corresponding to $\mathbf{b}$ to the $i$-th part in $A$, we take the $i$-th sum to be the cost for this edge. \ty{Need to think how to rewrite this}. The resulting sum has a nonzero value With the specified network and constraints, we solve this problem with an integer constrained linear program. We choose $\XBs$ to be all the deformation origin candidates in $A$ that have an outgoing flow of at least $1$.
